The genomic impacts of drift and selection for hybrid performance in maize

### 2015-08-26 main.tex
editorial changes to 'integrating genetic and physical map'

\subsection*{Integrating the genetic and physical map}
%The interpretation of our results depends upon a genetic and physical map that is as accurate as possible. 
\rev Our simulation approach requires co-linear genetic and physical maps. We therefore took steps to improve the positions of the SNP markers on the genetic and physical maps relative to version 5A.59 of the maize genome assembly. 
The probable physical position of each SNP based was obtained by comparing SNP context sequences to the genome sequence. 
For this purpose, SNP context sequences were defined as the sequence 25 bp upstream of the SNP, the bp representing the SNP itself, followed by 25 bp downstream of the SNP, making a total sequence length of 51bp. 
When a single genomic location was queried by two separate probes on the array, we chose the probe with higher quality calls and dropped the other marker from the dataset. 
To assign a genetic position for each SNP, we used a map derived from the B73xMo17 (IBM) mapping population similar to the IBM framework map in \citet{ganal2011a-large}. 
This genetic map contains 4,217 framework SNP markers, which provides a much higher density than the map used to order the 5A.59 release of the maize genome sequence. 
As a result, we identified several places in the genome where the physical positions were incorrect according to our genetic map. 
These cases included both simple reversals of the physical map relative to the genetic map, and also the assignment of blocks of markers to the wrong linkage group, which we refer to as mis-mapped blocks. 
To maintain collinearity between the genetic and physical map, the physical positions of these SNPs were reassigned as follows. 
Individual mis-mapped markers small reversals and mis-mapped blocks ($<10$ kb) were removed from the data. 
Small rearrangements of this sort are more likely to represent mis-mapped paralagous sequence than true errors in the physical map. 
When larger reversals were identified, we transposed the physical positions of the SNPs from one end of the segment to the other. 
Mis-mapped blocks were often larger than the physical gap into which they were moved. 
We therefore assigned the first SNP of the block to a position 10 kb downstream from the previous SNP on the correct linkage group. 
We then recalculated genomic coordinates for the rest of the chromosome based on the marker distances within the translocated segment. 
The last SNP of the block was also given a 10 kb cushion between itself and the next SNP on the correct linkage group. 
\rev Non-framework SNPs which had a physical position but no genetic coordinates were moved along with their framework neighbors if the nearest flanking framework markers were also moved.
However, it is unclear whether non-framework SNPs just outside of these anchors should be kept in place or moved along with the adjacent SNPs. 
Since most inversions were small relative to the genetic map (and would therefore still fall in the same window of a sliding window analysis), these SNPs were left in place. 
However, markers bordering translocations were removed to ensure there were no markers mapped to the incorrect linkage group. 
\rev Among the SNPs used for analyses, 15 were mis-mapped to a different linkage group and 1,585 were moved within a linkage group.
%Only a portion of the SNPs on the array had genetically mapped positions.

\rev Approximate genetic positions for non-framework SNPs were interpolated based on their physical positions with the approx() function in R \citep{rteam} with the 4,217 framework SNPs used as a reference.
%Unmapped SNPs were then assigned a genetic position by linear interpolation of genetic vs. physical distance using the approx() function in R \citep{rteam}. 
The IBM genetic map distances were then converted to single-meiosis map distances using the formulae of \citet{winkler2003determination}. 
Finally, SNPs located at physical positions outside of those bounded by the genetic map (such as the telomeres) were assigned the genetic position of their nearest mapped neighbor. 
Since moved segments were arbitrarily joined 10 kb from their nearest genetic neighbor, we acknowledge that the physical positions of these markers are only estimates. 
However, the estimated junctions are small relative to the genetic windows used for our analysis. 
The final map used is provided as supplemental material (Supplementary File S1).

>>>>

\subsection*{Integrating the genetic and physical map}
%The interpretation of our results depends upon a genetic and physical map that is as accurate as possible. 
\rev{Our simulation approach requires co-linear genetic and physical maps.}
We therefore took steps to improve the positions of the SNP markers on the genetic and physical maps relative to version 5A.59 of the maize genome assembly. 
The probable physical position of each SNP based was obtained by comparing SNP context sequences to the genome sequence. 
For this purpose, SNP context sequences were defined as the sequence 25 bp upstream of the SNP, the bp representing the SNP itself, followed by 25 bp downstream of the SNP, making a total sequence length of 51bp. 
When a single genomic location was queried by two separate probes on the array, we chose the probe with higher quality calls and dropped the other marker from the dataset. 
To assign a genetic position for each SNP, we used a map derived from the B73xMo17 (IBM) mapping population similar to the IBM framework map in \citet{ganal2011a-large}. 
This genetic map contains 4,217 framework SNP markers, which provides a much higher density than the map used to order the 5A.59 release of the maize genome sequence. 
As a result, we identified several places in the genome where the physical positions were incorrect according to our genetic map. 
These cases included both simple reversals of the physical map relative to the genetic map, and also the assignment of blocks of markers to the wrong linkage group, which we refer to as mis-mapped blocks. 
To maintain collinearity between the genetic and physical map, the physical positions of these SNPs were reassigned as follows. 
Individual mis-mapped markers small reversals and mis-mapped blocks ($<10$ kb) were removed from the data. 
Small rearrangements of this sort are more likely to represent mis-mapped paralagous sequence than true errors in the physical map. 
When larger reversals were identified, we transposed the physical positions of the SNPs from one end of the segment to the other. 
Mis-mapped blocks were often larger than the physical gap into which they were moved. 
We therefore assigned the first SNP of the block to a position 10 kb downstream from the previous SNP on the correct linkage group. 
We then recalculated genomic coordinates for the rest of the chromosome based on the marker distances within the translocated segment. 
The last SNP of the block was also given a 10 kb cushion between itself and the next SNP on the correct linkage group. 
\rev Non-framework SNPs which had a physical position but no genetic coordinates were moved along with their framework neighbors if the nearest flanking framework markers were also moved.
However, it is unclear whether non-framework SNPs just outside of these anchors should be kept in place or moved along with the adjacent SNPs. 
Since most inversions were small relative to the genetic map (and would therefore still fall in the same window of a sliding window analysis), these SNPs were left in place. 
However, markers bordering translocations were removed to ensure there were no markers mapped to the incorrect linkage group. 
\rev{Among the SNPs used for analyses, 15 were mis-mapped to a different linkage group and 1,585 were moved within a linkage group.}
%Only a portion of the SNPs on the array had genetically mapped positions.

\rev{Approximate genetic positions for non-framework SNPs were interpolated based on their physical positions with the approx() function in R \citep{rteam} with the 4,217 framework SNPs used as a reference.}
%Unmapped SNPs were then assigned a genetic position by linear interpolation of genetic vs. physical distance using the approx() function in R \citep{rteam}. 
The IBM genetic map distances were then converted to single-meiosis map distances using the formulae of \citet{winkler2003determination}. 
Finally, SNPs located at physical positions outside of those bounded by the genetic map (such as the telomeres) were assigned the genetic position of their nearest mapped neighbor. 
Since moved segments were arbitrarily joined 10 kb from their nearest genetic neighbor, we acknowledge that the physical positions of these markers are only estimates. 
However, the estimated junctions are small relative to the genetic windows used for our analysis. 
The final map used is provided as supplemental material (Supplementary File S1).
